Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-03-23 paper/ms.tex
Add initial gas disk scale height

>>>>

{\bf We measured the initial scale height of the gas disk in a bin extending from
$R=8\,\textrm{kpc}$ to $R=8.5\,\textrm{kpc}$. The vertical profile is well-fit
by a Gaussian with a scale height of $97\,\textrm{pc}$. This is somewhat lower
than the observed value in the HI disk of $\sim200\,\textrm{kpc}$
\citep{1995ApJ...448..138M}.}
